---
title: "Three-Outcome Simulation Code"
output: html_document
date: '2024-04-04'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggpubr)
library(ggplot2)
library(gridExtra)
library(cowplot)
library(grid)
library(DiagrammeR)
library(nnet)
# for performance comparison
library(mclust)
library(kernlab)
library(kohonen)
library(class)
library(mclust)
library(clue) # NMI
library(cluster)
library(fpc) # RI
library(tibble)
library(dplyr)
library(tidyr)
library(MOTRL)

setwd("R")
source("Benefit_gain.R")
source("best.H.R")
source("MO_Tree_Chang.R")
source("predict_leaf.R")
source("Reg.mu.R")
source("Split.X.R")
source("visualization.R")
source("vis_tree.R")

source("mus.AIPW.R")
source("M.propen.R")
Custom.color = c("#CD2626","#79aec1","#2E8B57","#d6b55a")

map_to_consecutive = function(x) {
  mapped_values = match(x, unique(x))
  return(mapped_values)
}
```


## YS update simulation function with new designed pareto dominances

```{r}
Simulation_MOTree_3 = function(iter = 100, n.cov = 5, n.per.group = 100) {
  
  nmi_results = rep(list(rep(NA, iter)),7) 
  ari_results = rep(list(rep(NA, iter)),7) 
  weights <- expand.grid(seq(0, 1, by = 0.2), seq(0, 1, by = 0.2)) %>%
    filter(Var1 + Var2 <= 1) %>%
    mutate(Var3 = round((1 - Var1 - Var2), 1))
  
  for (w_idx in 1:nrow(weights)) {
    assign(paste0("avg_cf_results", w_idx), rep(list(rep(NA, iter)),7) )
    assign(paste0("true_optimal_weighted_mean", w_idx), numeric(iter))  
    assign(paste0("non_dominant_results", w_idx), rep(list(rep(NA, iter)), 7))  
    
  }
  
  for (i in c(1:iter)) {
    
    ###########################################
    ############ Data generation ##############
    ###########################################
    set.seed(412 + i)
    k = 4 # number of treatment
    n_grp = 8  # Number of groups
    total_patients <- n.per.group * n_grp
        
    # group = rep(1:4, each = n.per.group)
    groups <- 1:n_grp   # Total groups
    group <- rep(groups, each = n.per.group)

    
    X <- matrix(NA, nrow = n.per.group * n_grp, ncol = j)
    X[, 1] <- rnorm(n.per.group * n_grp, 0, 0.05) + (group - 1) / 5
    X[, 2] <- rnorm(n.per.group * n_grp, mean = 0, sd = 0.05) - 0.5 * (group - 4)
    for (jj in 3:j) {
      X[, jj] <- rnorm(n.per.group * n_grp, mean = 0, sd = 0.05)
    }
    
    # m1 <- c(4, 1, 0.5, 0, 3, 0, 0.5, 0, 4, 0, 0.5, 1)   # Treatment 1 dominates for Group 1 and 2
    # m2 <- c(4, 0, 0, 1.5, 3, 0.5, 0, 0.5, 4, 1, 0, 0.5)   # Same dominance structure as Group 1
    # m3 <- c(4, 3, 2, 1, 3, 2, 1, 0, 4, 3, 1, 1)   # Treatments 1 and 2 dominate
    # m4 <- c(3, 3, 3, 2, 4, 4, 4, 2, 3, 3, 2, 1)   # Treatments 2 and 3 dominate
    # m5 <- c(1, 0.5, 0, 4, 0, 0, 1, 4, 0.5, 0, 1, 4)   # Treatment 4 dominates for Group 5 and 6
    # m6 <- c(1.5, 1, 1.5, 4, 1, 1.5, 0, 4, 0, 1, 0, 4)   # Same dominance structure as Group 5
    # m7 <- c(0, 0, 4, 4, 1, 1, 4, 4, 0, 0, 4, 5)   # Treatments 3 and 4 dominate
    # m8 <- c(0, 4, 0, 4, 1, 5, 1, 4, 0, 4, 0, 4)   # Treatments 2 and 4 dominate
    m1 <- c(4, 1, 0.5, 0, 3, 0, 1.5, 0, 4, 0, 0.5, 1)   # Treatment 1 dominates for Group 1 and 2
    m2 <- c(4, 0, 0, 1.5, 3, 0.5, 0, 0.5, 4, 1, 0, 0.5)   # Same dominance structure as Group 1
    m3 <- c(3, 1.5, 0.5, 0, 4, 0, 0, 1, 4, 1, 2, 0.5)    # Treatments 1 and 2 dominate
    m4 <- c(4, 3, 2, 1, 1, 4, 1, 4, 2.5, 3, 0, 1)   # Treatments 2 and 3 dominate
    m5 <- c(1, 0.5, 0, 4, 2, 0, 1, 4, 0.5, 0, 1, 4)   # Treatment 4 dominates for Group 5 and 6
    m6 <- c(1.5, 1, 0.5, 4, 1, 1.5, 0, 4, 2, 1, 0, 4)   # Same dominance structure as Group 5
    m7 <- c(0, 0, 4, 2.5, 0, 1, 3, 2, 0, 0, 4, 1)   # Treatments 3 and 4 dominate
    m8 <- c(0, 4, 0, 2, 0, 1, 0, 2, 0.5, 2.5, 3, 4)   # Treatments 2 and 4 dominate
    list_m <- list(m1, m2, m3, m4, m5, m6, m7, m8)
    
    Y <- matrix(0, n.per.group * n_grp, 3 * k)
    for (ii in 1:(n.per.group * n_grp)) {
      ind <- group[ii]
      Y[ii, ] <- list_m[[ind]] +
        X[ii, 1] * 0.1 +
        X[ii, 2] * 0.05 +
        X[ii, 3] * -0.0005 +
        X[ii, 4] * 0.0001 +
        X[ii, 5] * -0.0001 +
        rnorm(12, 0, 0.3)
    }
    Y1 <- Y[, c(1, 4, 7, 10)]
    Y2 <- Y[, c(2, 5, 8, 11)]
    Y3 <- Y[, c(3, 6, 9, 12)]
    
    true_treatment <- sample(1:k, n.per.group * n_grp, replace = TRUE)
    Y1.obs <- sapply(1:(n.per.group * n_grp), function(i) Y1[i, true_treatment[i]])
    Y2.obs <- sapply(1:(n.per.group * n_grp), function(i) Y2[i, true_treatment[i]])
    Y3.obs <- sapply(1:(n.per.group * n_grp), function(i) Y3[i, true_treatment[i]])
    
    df_obs <- data.frame(
      Y1_obs = Y1.obs,
      Y2_obs = Y2.obs,
      Y3_obs = Y3.obs,
      Treat_num = true_treatment,
      Group = factor(group)
    )
    df_obs$true_Group <- case_when(
      df_obs$Group %in% c(1, 2, 3) ~ 1,
      df_obs$Group %in% c(4) ~ 2,
      df_obs$Group %in% c(5, 6) ~ 3,
      df_obs$Group %in% c(7) ~ 4,
      df_obs$Group %in% c(8) ~ 5
    )
    df_obs$Treatment <- as.factor(case_when(
      df_obs$Treat_num == 1 ~ "A",
      df_obs$Treat_num == 2 ~ "B",
      df_obs$Treat_num == 3 ~ "C",
      df_obs$Treat_num == 4 ~ "D"
    ))
    for (cov in 1:j) {
      df_obs[[paste0("X", cov)]] <- X[, cov]
    }
    # X <- matrix(NA, nrow = n.per.group * n_grp, ncol = n.cov)
    # X[, 1] <- rnorm(n.per.group * n_grp, 0, 0.05) + (group - 1) / 3
    # X[, 2] <- rnorm(n.per.group * n_grp, mean = 0, sd = 0.05) - 0.5 * (group - 2)
    # for (k in 3:n.cov) {
    #   X[, k] <- rnorm(n.per.group * n_grp, mean = 0, sd = 0.05)
    # }
    # 
    # n_Y <- 3  # Number of outcomes (Y1, Y2, Y3)
    # Parameter <- matrix(rnorm(n_grp * k * n_Y, 0, 1), nrow = n_grp, ncol = k * n_Y)
    # Y <- matrix(0, nrow = n.per.group * n_grp, ncol = k * n_Y)
    # for (ii in 1:(n.per.group * n_grp)) {
    #   ind <- group[ii]
    #   Y[ii, ] <- Parameter[ind, ] + 
    #     rnorm(k * n_Y, 0, 0.2)
    # }
    # Y_record <- lapply(1:n_Y, function(yy) Y[, ((yy - 1) * k + 1):(yy * k)])
    # Y1 <- Y_record[[1]]
    # Y2 <- Y_record[[2]]
    # Y3 <- Y_record[[3]]
    # 
    # 
    # true_treatment <- sample(1:k, n.per.group * n_grp, replace = TRUE)
    # Y1.obs <- sapply(1:(n.per.group * n_grp), function(i) Y1[i, true_treatment[i]])
    # Y2.obs <- sapply(1:(n.per.group * n_grp), function(i) Y2[i, true_treatment[i]])
    # Y3.obs <- sapply(1:(n.per.group * n_grp), function(i) Y3[i, true_treatment[i]])
    # 
    # df_obs <- data.frame(
    #   Y1_obs = Y1.obs,
    #   Y2_obs = Y2.obs,
    #   Y3_obs = Y3.obs,
    #   Treat_num = true_treatment,
    #   Group = factor(group)
    # )
    # 
    # # df_obs$Treatment <- factor(
    # #   df_obs$Treat_num,
    # #   labels = c("A", "B", "C", "D")
    # # )
    # df_obs$Treatment = as.factor(case_when(df_obs$Treat_num == 1 ~ "A",
    #                                        df_obs$Treat_num == 2 ~ "B",
    #                                        df_obs$Treat_num == 3 ~ "C",
    #                                        df_obs$Treat_num == 4 ~ "D"))
    # 
    # for (cov in 1:n.cov) {
    #   df_obs[[paste0("X", cov)]] <- X[, cov]
    # }
    
    ####### Pareto Dominance Evaluation #######
    non_dominant_treatments <- lapply(1:total_patients, function(patient) {
      outcomes <- cbind(Y1[patient, ], Y2[patient, ], Y3[patient, ])  
      is_non_dominated <- function(outcomes) {
        apply(outcomes, 1, function(x) {
          !any(apply(outcomes, 1, function(y) all(y >= x) & any(y > x)))
        })
      }
      pareto_front <- which(is_non_dominated(outcomes))
      return(pareto_front)  
    })
    
    ## true optimal weighted conterfactual mean
    for (w_idx in 1:nrow(weights)) {
      w <- as.numeric(weights[w_idx, ])
      
      # Weighted counterfactual outcomes for all treatments
      Y_w <- w[1] * Y1 + w[2] * Y2 + w[3] * Y3
      # Maximum weighted counterfactual outcome for each individual (Y*_opt)
      max_weighted_outcomes <- apply(Y_w, 1, max)
      assign(paste0("true_optimal_weighted_mean", w_idx),
             replace(get(paste0("true_optimal_weighted_mean", w_idx)), i, mean(max_weighted_outcomes)))
    }
    
    
    
    ###########################################
    ########## Clustering methods #############
    ###########################################
    
    ## MOTree
    Cov = df_obs %>% dplyr::select(starts_with("X"))
    treeout = DTRtree(Ys = cbind(df_obs$Y1_obs, df_obs$Y2_obs, df_obs$Y3_obs),
                      A = df_obs$Treat_num,
                      H = Cov,
                      pis.hat=NULL,
                      mus.reg=NULL,
                      depth=2,
                      minsplit=20,
                      w_vec = as.matrix(weights),
                      weight_combine = "mean",
                      lambda = 0.05)
    leaf_pred = predict_leaf.DTR(treeout, newdata = Cov)
    df_obs$group.MOTree = map_to_consecutive(leaf_pred)
    
    SimuData = df_obs %>% dplyr::select(# Y1_obs, Y2_obs, 
      # Treat_num, 
      starts_with("X"))
    
    ## K-means 
    kmeans_result3 = kmeans(SimuData, centers = 3)  # Assuming 3 clusters
    kmeans_result4 = kmeans(SimuData, centers = 4)  # Assuming 3 clusters
    df_obs$group.kmeans3 = kmeans_result3$cluster
    df_obs$group.kmeans4 = kmeans_result4$cluster
    
    ## Hierarchical
    hc_result = hclust(dist(SimuData), method = "ward.D") # "ward.D2")
    hc_clusters = cutree(hc_result, k = 3) # k = 4)
    df_obs$group.hc = hc_clusters
    
    ## GMM
    gmm_result = Mclust(SimuData) 
    df_obs$group.gmm = gmm_result$classification 
    
    ## Spectral Clustering
    spectral_result = specc(as.matrix(SimuData), centers = 4)  # Assuming 4 clusters
    df_obs$group.spectral = spectral_result@.Data
    
    ## Self-Organizing Map (SOM)
    som_grid = kohonen::somgrid(xdim = 2, ydim = 2, topo = "rectangular")
    som_model = kohonen::som(as.matrix(SimuData), grid = som_grid, rlen = 100)
    som_clusters = cutree(hclust(dist(som_model$codes[[1]])), k = 4)  
    som_result = som_model$unit.classif
    df_obs$group.som = som_clusters[som_result]
    
    ###########################################
    ############ Begin comparison #############
    ###########################################
    true_labels_nmi = as.cl_partition(df_obs$true_Group)     
    true_labels_ari = as.numeric(df_obs$true_Group)      
    clustering_methods = list(
      MOTree = df_obs$group.MOTree,
      # MOTRL = NA,
      HC = df_obs$group.hc,
      GMM = df_obs$group.gmm,
      KMeans3 = df_obs$group.kmeans3,
      KMeans4 = df_obs$group.kmeans4,
      Spectral = df_obs$group.spectral,
      SOM = df_obs$group.som
    )
    
    dist_matrix = dist(as.matrix(SimuData))
    
    for (method in seq_along(clustering_methods)) {
      method_name = names(clustering_methods)[method]
      pred_labels_nmi = as.cl_partition(clustering_methods[[method_name]])  
      pred_labels_ari = as.numeric(clustering_methods[[method_name]])    
      cluster_labels = as.numeric(clustering_methods[[method_name]])      
      nmi_results[[method]][i] = as.numeric(cl_agreement(true_labels_nmi, 
                                                         pred_labels_nmi, 
                                                         method = "NMI"))
      ari_results[[method]][i] = cluster.stats(dist_matrix, true_labels_ari, 
                                               pred_labels_ari)$corrected.rand
      
      cluster_opt_trt = list()
      for (w_idx in 1:nrow(weights)) {
        w <- as.numeric(weights[w_idx, ])
        Y_w <- w[1] * Y1 + w[2] * Y2 + w[3] * Y3
        
        # find cluster-based optimal treatment for each individual (by each of the methods)
        cluster_opt_trt[[method]] = sapply(unique(cluster_labels), 
                                           function(cluster) {
                                             cluster_ids = which(cluster_labels == cluster)
                                             avg_outcomes = colMeans(Y_w[cluster_ids, , drop = FALSE])
                                             which.max(avg_outcomes)  
                                           })
        
        df_obs[[paste0("opt_trt_", method_name, "_w", w_idx)]] = sapply(cluster_labels,
                                                                        function(cluster) cluster_opt_trt[[method]][cluster]) 
        df_obs[[paste0("cf_", method_name, "_w", w_idx)]] = sapply(1:nrow(Y_w), 
                                                                   function(x) Y_w[x, df_obs[[paste0("opt_trt_", method_name, "_w", w_idx)]][x]])
        
        avg_cf_results <- get(paste0("avg_cf_results", w_idx))
        avg_cf_results[[method]][i] <- mean(df_obs[[paste0("cf_", method_name, "_w", w_idx)]], na.rm = T)
        assign(paste0("avg_cf_results", w_idx), avg_cf_results)
        
        
        
        ## YS ADD THIS NEW FOR NEW MATRIC 11/25/2024
        ## Predicted optimal treatment for current weight
        pred_opt_trt <- df_obs[[paste0("opt_trt_", method_name, "_w", w_idx)]]
        is_non_dominant <- sapply(seq_len(n.per.group * 4), function(patient) {
          pred_opt_trt[patient] %in% non_dominant_treatments[[patient]]
        })
        non_dominant_results <- get(paste0("non_dominant_results", w_idx))
        non_dominant_results[[method]][i] <- mean(is_non_dominant, na.rm = T)
        assign(paste0("non_dominant_results", w_idx), non_dominant_results)
        
        cluster_opt_trt = list() 
        
      }
      
    }
    
    
    
  }
  
  # evaluation
  nmi_mean = round(as.numeric(lapply(nmi_results, mean)),3)
  nmi_sd = round(as.numeric(lapply(nmi_results, sd)),3)
  ari_mean = round(as.numeric(lapply(ari_results, mean)),3)
  ari_sd = round(as.numeric(lapply(ari_results, sd)),3)
  nmi_out = paste0(nmi_mean, "(", nmi_sd, ")")
  ari_out = paste0(ari_mean, "(", ari_sd, ")")
  
  # non_dominant_summary <- matrix(NA, nrow = length(clustering_methods), ncol = nrow(weights))
  # rownames(non_dominant_summary) <- names(clustering_methods)
  #   # paste0("Method_", 1:7)  # Adjust according to actual method names
  # colnames(non_dominant_summary) <- paste0("Weight_", 1:nrow(weights))
  
  
  
  
  # weight specific results
  for (w_idx in 1:nrow(weights)) {
    
    avg_cf_results <- get(paste0("avg_cf_results", w_idx))
    assign(paste0("avg_cf_mean", w_idx), 
           round(as.numeric(lapply(avg_cf_results, mean)), 3))
    assign(paste0("avg_cf_sd", w_idx), 
           round(as.numeric(lapply(avg_cf_results, sd)), 3))
    assign(paste0("avg_cf_out", w_idx), 
           paste0(get(paste0("avg_cf_mean", w_idx)), 
                  "(", get(paste0("avg_cf_sd", w_idx)), ")"))
    
    non_dominant_means <- get(paste0("non_dominant_results", w_idx)) # [[method]]
    # non_dominant_summary[method, w_idx] <- mean(non_dominant_means)
    assign(paste0("non_dominant_mean", w_idx), 
           round(as.numeric(lapply(non_dominant_means, mean)), 3))
    assign(paste0("non_dominant_sd", w_idx), 
           round(as.numeric(lapply(non_dominant_means, sd)), 3))
    assign(paste0("non_dominant_out", w_idx), 
           paste0(get(paste0("non_dominant_mean", w_idx)), 
                  "(", get(paste0("non_dominant_sd", w_idx)), ")"))
  }
  
  
  true_optimal_weighted_means <- sapply(1:nrow(weights), function(w_idx) {
    mean(get(paste0("true_optimal_weighted_mean", w_idx)))
  })
  true_optimal_weighted_means <- t(data.frame(true_optimal_weighted_means))
  rownames(true_optimal_weighted_means) <- "True_Optimal_Mean"
  colnames(true_optimal_weighted_means) <- paste0("Weight_", 1:nrow(weights))# seq(0, 1, by = 0.1))
  
  
  clust_perform = data.frame(NMI = nmi_out,
                             ARI = ari_out)
  row.names(clust_perform) = names(clustering_methods)
  
  cf_Y_perform = data.frame(
    avg_cf_w1 = avg_cf_out1,
    avg_cf_w2 = avg_cf_out2,
    avg_cf_w3 = avg_cf_out3,
    avg_cf_w4 = avg_cf_out4,
    avg_cf_w5 = avg_cf_out5,
    avg_cf_w6 = avg_cf_out6,
    avg_cf_w7 = avg_cf_out7,
    avg_cf_w8 = avg_cf_out8,
    avg_cf_w9 = avg_cf_out9,
    avg_cf_w10 = avg_cf_out10,
    avg_cf_w11 = avg_cf_out11,
    avg_cf_w12 = avg_cf_out12,
    avg_cf_w13 = avg_cf_out13,
    avg_cf_w14 = avg_cf_out14,
    avg_cf_w15 = avg_cf_out15,
    avg_cf_w16 = avg_cf_out16,
    avg_cf_w17 = avg_cf_out17,
    avg_cf_w18 = avg_cf_out18,
    avg_cf_w19 = avg_cf_out19,
    avg_cf_w20 = avg_cf_out20, 
    avg_cf_w21 = avg_cf_out21)
  row.names(cf_Y_perform) = names(clustering_methods)
  
  
  
  non_dominant_perform = data.frame(
    non_dominant_w1 = non_dominant_out1,
    non_dominant_w2 = non_dominant_out2,
    non_dominant_w3 = non_dominant_out3,
    non_dominant_w4 = non_dominant_out4,
    non_dominant_w5 = non_dominant_out5,
    non_dominant_w6 = non_dominant_out6,
    non_dominant_w7 = non_dominant_out7,
    non_dominant_w8 = non_dominant_out8,
    non_dominant_w9 = non_dominant_out9,
    non_dominant_w10 = non_dominant_out10,
    non_dominant_w11 = non_dominant_out11,
    non_dominant_w12 = non_dominant_out12,
    non_dominant_w13 = non_dominant_out13,
    non_dominant_w14 = non_dominant_out14,
    non_dominant_w15 = non_dominant_out15,
    non_dominant_w16 = non_dominant_out16,
    non_dominant_w17 = non_dominant_out17,
    non_dominant_w18 = non_dominant_out18,
    non_dominant_w19 = non_dominant_out19,
    non_dominant_w20 = non_dominant_out20,
    non_dominant_w21 = non_dominant_out21)
  row.names(non_dominant_perform) = names(clustering_methods)
  
  cf_Y_names = c(paste0("avg_cf_mean", 1:nrow(weights)), 
                 paste0("avg_cf_sd", 1:nrow(weights)))
  cf_Y = as.data.frame(mget(cf_Y_names))
  row.names(cf_Y) = names(clustering_methods)
  
  non_dominant_names = c(paste0("non_dominant_mean", 1:nrow(weights)), 
                         paste0("non_dominant_sd", 1:nrow(weights)))
  non_dominant = as.data.frame(mget(non_dominant_names))
  row.names(non_dominant) = names(clustering_methods)
  
  
  return(list(clust_perform = clust_perform,
              # cf_Y_perform = cf_Y_perform,
              # non_dominant_perform = non_dominant_perform,
              cf_Y = cf_Y,
              true_optimal_weighted_means = true_optimal_weighted_means,
              non_dominant = non_dominant
  ))
}


# smaller sample size
three_outcome_result50 = Simulation_MOTree_3(iter = 100, n.cov = 5, n.per.group = 50)
three_outcome_result50

# larger sample size
three_outcome_result100 = Simulation_MOTree_3(iter = 5, n.cov = 5, n.per.group = 100)
three_outcome_result100

# larger sample size
three_outcome_result200 = Simulation_MOTree_3(iter = 5, n.cov = 5, n.per.group = 200)
three_outcome_result200
```

## performance Evaluation

### Clustering Performance

```{r}
three_outcome_result50$clust_perform
three_outcome_result50$cf_Y_perform
three_outcome_result50$non_dominant_perform
```

```{r}
three_outcome_result100$clust_perform
three_outcome_result100$cf_Y_perform
three_outcome_result100$non_dominant_perform
```

```{r}
three_outcome_result200$clust_perform
three_outcome_result200$cf_Y_perform
three_outcome_result200$non_dominant_perform
```

### Visualization

Sample size = 4 * 50

$$Y_w^{*opt} - \hat Y_w^*$$
```{r}
# Extract outcomes from the simulation results
outcomes <- result50$cf_Y  # Counterfactual outcomes
true_opt_means <- result50$true_optimal_weighted_means  # 1x11 matrix of observed weighted outcomes

# Prepare the observed means for merging
true_opt_long <- as.data.frame(t(true_opt_means)) %>%
  rownames_to_column(var = "Weight") %>%
  rename(TrueOpt = True_Optimal_Mean) %>%
  mutate(Weight = as.numeric(gsub("Weight_", "", Weight)))

# Prepare the counterfactual mean outcomes and merge with observed means
outcomes_long <- outcomes %>%
  rownames_to_column(var = "Method") %>%
  pivot_longer(cols = starts_with("avg_cf_mean"), 
               names_to = "Weight", 
               values_to = "Mean") %>%
  mutate(Weight = as.numeric(gsub("avg_cf_mean", "", Weight)) * 0.1) %>%
  left_join(true_opt_long, by = "Weight") %>%
  mutate(Difference = Mean - TrueOpt)  # Calculate the difference between counterfactual and observed means

# Plot the differences
ggplot(outcomes_long, aes(x = Weight, y = Difference, color = Method, fill = Method)) +
  geom_smooth(method = "loess", se = TRUE, size = 1.2) +  # Smoothed line with CI for difference
  labs(title = "Difference between Estimated and True Optimal Conterfactual Outcome",
       x = "Weight on Y1",
       y = "Difference (Y_opt - Y_hat)") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )


```



```{r}
# Extract the non-dominant data from the simulation results
non_dominant <- result50$non_dominant

# Prepare the non-dominant data for plotting
non_dominant_long <- non_dominant %>%
  rownames_to_column(var = "Method") %>%
  pivot_longer(cols = starts_with("non_dominant_mean"), 
               names_to = "Weight", 
               values_to = "Mean") %>%
  mutate(Weight = as.numeric(gsub("non_dominant_mean", "", Weight)) * 0.1) %>%
  left_join(
    non_dominant %>%
      rownames_to_column(var = "Method") %>%
      pivot_longer(cols = starts_with("non_dominant_sd"), 
                   names_to = "Weight", 
                   values_to = "SD") %>%
      mutate(Weight = as.numeric(gsub("non_dominant_sd", "", Weight)) * 0.1),
    by = c("Method", "Weight")
  )

# Plot the percentage of non-dominance
ggplot(non_dominant_long, aes(x = Weight, y = Mean, color = Method, fill = Method)) +
  geom_line(size = 1.2) +  # Line for the mean percentage of non-dominance
  geom_ribbon(aes(ymin = Mean - 1.96*SD/sqrt(200), ymax = Mean + 1.96*SD/sqrt(200)), alpha = 0.2, linetype = 0) +  # Add shadow for SD
  labs(title = "Percentage of Non-Dominance of the Estimated Optimal Treatment",
       x = "Weight on Y1",
       y = "Percentage of Non-Dominance") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )

```




Sample size = 4 * 500

$$Y_w^{*opt} - \hat Y_w^*$$
```{r}
# Extract outcomes from the simulation results
outcomes <- result500$cf_Y  # Counterfactual outcomes
true_opt_means <- result500$true_optimal_weighted_means  # 1x11 matrix of observed weighted outcomes

# Prepare the observed means for merging
true_opt_long <- as.data.frame(t(true_opt_means)) %>%
  rownames_to_column(var = "Weight") %>%
  rename(TrueOpt = True_Optimal_Mean) %>%
  mutate(Weight = as.numeric(gsub("Weight_", "", Weight)))

# Prepare the counterfactual mean outcomes and merge with observed means
outcomes_long <- outcomes %>%
  rownames_to_column(var = "Method") %>%
  pivot_longer(cols = starts_with("avg_cf_mean"), 
               names_to = "Weight", 
               values_to = "Mean") %>%
  mutate(Weight = as.numeric(gsub("avg_cf_mean", "", Weight)) * 0.1) %>%
  left_join(true_opt_long, by = "Weight") %>%
  mutate(Difference = Mean - TrueOpt)  # Calculate the difference between counterfactual and observed means

# Plot the differences
ggplot(outcomes_long, aes(x = Weight, y = Difference, color = Method, fill = Method)) +
  geom_smooth(method = "loess", se = TRUE, size = 1.2) +  # Smoothed line with CI for difference
  labs(title = "Difference between Estimated and True Optimal Conterfactual Outcome",
       x = "Weight on Y1",
       y = "Difference (Y_opt - Y_hat)") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )


```



```{r}
# Extract the non-dominant data from the simulation results
non_dominant <- result500$non_dominant

# Prepare the non-dominant data for plotting
non_dominant_long <- non_dominant %>%
  rownames_to_column(var = "Method") %>%
  pivot_longer(cols = starts_with("non_dominant_mean"), 
               names_to = "Weight", 
               values_to = "Mean") %>%
  mutate(Weight = as.numeric(gsub("non_dominant_mean", "", Weight)) * 0.1) %>%
  left_join(
    non_dominant %>%
      rownames_to_column(var = "Method") %>%
      pivot_longer(cols = starts_with("non_dominant_sd"), 
                   names_to = "Weight", 
                   values_to = "SD") %>%
      mutate(Weight = as.numeric(gsub("non_dominant_sd", "", Weight)) * 0.1),
    by = c("Method", "Weight")
  )

# Plot the percentage of non-dominance
ggplot(non_dominant_long, aes(x = Weight, y = Mean, color = Method, fill = Method)) +
  geom_line(size = 1.2) +  # Line for the mean percentage of non-dominance
  geom_ribbon(aes(ymin = Mean - 1.96*SD/sqrt(200), ymax = Mean + 1.96*SD/sqrt(200)), alpha = 0.2, linetype = 0) +  # Add shadow for SD
  labs(title = "Percentage of Non-Dominance of the Estimated Optimal Treatment",
       x = "Weight on Y1",
       y = "Percentage of Non-Dominance") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )

```







# 12/02/2024 YS to do:

Three outcome scenario

- [Table for clustering results] 

- [Figure for counterfactrual outcome and dominance]


**Add more scenarios**

- [add to Table 1 as new chunks] design other scenarios with different sample size? noise? covaraite structure
Sample sizes: 50, 100, 200
Current noise: Normal(0, 0.3)
Current covaraites: 5



