---
title: "multiple tree clustering toy example"
output: html_document
date: '2024-04-04'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggpubr)
library(ggplot2)
library(gridExtra)
library(cowplot)
library(grid)
library(DiagrammeR)
library(nnet)
# for performance comparison
library(mclust)
library(kernlab)
library(kohonen)
library(class)
library(mclust)
library(clue) # NMI
library(cluster)
library(fpc) # RI

setwd("R")
source("Benefit_gain.R")
source("best.H.R")
source("MO_Tree_Chang.R")
source("predict_leaf.R")
source("Reg.mu.R")
source("Split.X.R")
source("visualization.R")
source("vis_tree.R")

source("mus.AIPW.R")
source("M.propen.R")
Custom.color = c("#CD2626","#79aec1","#2E8B57","#d6b55a")
```





## YS update 10/28/2024

Randomly assign true treatments and simulate the observed outcomes 
```{r}
set.seed(412)
k = 4
n = 100
j = 5  # Number of covariates
group = rep(1:4, each = n)

# We think that group 1 and 2 are the same patients regarding 


########## Generating covariates
### chang's single X
# X1 = rnorm(n*4,0,0.05) + (group-1)/3
# plot(density(X1, from = -0.2, to = 1.2), main = "Density of X1")

### YS first temp
# X = matrix(rnorm(n * 4 * j, 0, 0.05), nrow = n * 4, ncol = j)

### YS second temp
X = matrix(NA, nrow = n * 4, ncol = j)
X[, 1] = rnorm(n*4,0,0.05) + (group-1)/3
X[, 2] = rnorm(n * 4, mean = 0, sd = 0.05) - 0.5 * (group - 2) 
for (k in 3:j) {
  X[, k] = rnorm(n * 4, mean = 0, sd = 0.05)
}


plot(density(X[,1], from = -0.2, to = 1.2), main = "Density of X1")
plot(density(X[,2], from = -0.2, to = 1.2), main = "Density of X2")


m1 = c(1, 0, 0, 1, -1, 0, 0, -1)
m2 = c(1, 0, 0, 1, 0, -1, -1, 0)
m3 = c(0, -1, 1, 0, 0, 1, -1, 0)
m4 = c(-1, 0, 0, -1, 1, 0, 0, 1)
list_m = list(m1 = m1, m2 = m2, m3 = m3, m4 = m4)
Y = matrix(0, n * 4, 2 * 4)
for (ii in 1:(4 * n)) {
  ind = group[ii]
  Y[ii, ] = list_m[[ind]] + 
            X[ii, 1] * 0.1 +  
            X[ii, 2] * 0.05 +  
            X[ii, 3] * -0.0005 + 
            X[ii, 4] * 0.0001 +  
            X[ii, 5] * -0.0001 + 
            rnorm(8, 0, 0.3)  
}
Y1 = Y[, c(1, 3, 5, 7)]
Y2 = Y[, c(2, 4, 6, 8)]

# Generating the obserevd data
true_treatment = sample(1:4, n * 4, replace = TRUE)
Y1.obs = sapply(1:(n * 4), function(i) Y1[i, true_treatment[i]])
Y2.obs = sapply(1:(n * 4), function(i) Y2[i, true_treatment[i]])

df_obs = data.frame(
  Y1_obs = Y1.obs,
  Y2_obs = Y2.obs,
  Treat_num = true_treatment,
  Group = factor(group)
)
df_obs$Treatment = as.factor(case_when(df_obs$Treat_num == 1 ~ "A",
                                       df_obs$Treat_num == 2 ~ "B",
                                       df_obs$Treat_num == 3 ~ "C",
                                       df_obs$Treat_num == 4 ~ "D"))
for (cov in 1:j) {
  df_obs[[paste0("X", cov)]] = X[, cov]
}

ggplot(data = df_obs, aes(x = Y1_obs, y = Y2_obs, color = Treatment)) +
  geom_point() +
  facet_wrap(~Group) +
  ylab("Observed Outcome 2") +
  xlab("Observed Outcome 1")

head(df_obs)
```


YS update for 8 treatment scenario
```{r}
set.seed(412)
k = 8
n = 100
j = 5  # Number of covariates
group = rep(1:8, each = n.per.group)
X = matrix(NA, nrow = n.per.group * 8, ncol = n.cov)
X[, 1] = rnorm(n.per.group* 8,0,0.05) + (group-1)/3
X[, 2] = rnorm(n.per.group * 8, mean = 0, sd = 0.05) - 0.5 * (group - 2) 
for (k in 3:n.cov) {
  X[, k] = rnorm(n.per.group * 8, mean = 0, sd = 0.05)
}
m1 = c(3, 2, 4, 2, 2, 1, 1, 2, 
       3.5, 3.5, 2, 4, 1, 3.5, 2, 3)
m2 = c(2, 4, 3.5, 3.5, 4, 2, 1, 3.5, 
       1, 2, 2, 3, 2, 1, 3, 2)
m3 = c(2, 4, 3.5, 3.5, 4, 2, 2, 1, 
       1, 2, 2, 3, 3, 2, 1, 3.5)
m3 = c(2, 4, 3.5, 3.5, 4, 2, 2, 1, 
       1, 2, 2, 3, 3, 2, 1, 3.5) # YS to update 8 trt scenario

m4 = c(-1, 0, 0, -1, 1, 0, 0, 1)
m5 = c(1, 0, 0, 1, -1, 0, 0, -1)
m6 = c(1, 0, 0, 1, 0, -1, -1, 0)
m7 = c(0, -1, 1, 0, 0, 1, -1, 0)
m8 = c(-1, 0, 0, -1, 1, 0, 0, 1)
list_m = list(m1 = m1, m2 = m2, m3 = m3, m4 = m4, 
              m5 = m5, m6 = m6, m7 = m7, m8 = m8)
Y = matrix(0, n.per.group * 8, 2 * 8)
for (ii in 1:(8 * n.per.group)) {
  ind = group[ii]
  Y[ii, ] = list_m[[ind]] + 
    X[ii, 1] * 0.1 +  
    X[ii, 2] * 0.05 +  
    X[ii, 3] * -0.0005 + 
    X[ii, 4] * 0.0001 +  
    X[ii, 5] * -0.0001 + 
    rnorm(8, 0, 0.3)  
}
Y1 = Y[, c(1, 3, 5, 7, 9, 11, 13, 15)]
Y2 = Y[, c(2, 4, 6, 8, 10, 12, 14, 16)]

true_treatment = sample(1:4, n.per.group * 8, replace = TRUE)
Y1.obs = sapply(1:(n.per.group * 8), function(i) Y1[i, true_treatment[i]])
Y2.obs = sapply(1:(n.per.group * 8), function(i) Y2[i, true_treatment[i]])

df_obs = data.frame(
  Y1_obs = Y1.obs,
  Y2_obs = Y2.obs,
  Treat_num = true_treatment,
  Group = factor(group)
)
df_obs$Treatment = as.factor(case_when(df_obs$Treat_num == 1 ~ "A",
                                       df_obs$Treat_num == 2 ~ "B",
                                       df_obs$Treat_num == 3 ~ "C",
                                       df_obs$Treat_num == 4 ~ "D"))
for (cov in 1:j) {
  df_obs[[paste0("X", cov)]] = X[, cov]
}

ggplot(data = df_obs, aes(x = Y1_obs, y = Y2_obs, color = Treatment)) +
  geom_point() +
  facet_wrap(~Group) +
  ylab("Observed Outcome 2") +
  xlab("Observed Outcome 1")

head(df_obs)
```







generate conditional mean Y
fit working model E(Y|X,A)
estimate pseudo outcome Yhat under 4 As => input
working_model = list() / NULL

```{r}
w0 = seq(0,1,0.02) 
Cov = df_obs %>% dplyr::select(starts_with("X"))
treeout = DTRtree(Ys = cbind(df_obs$Y1_obs, df_obs$Y2_obs), 
        A = df_obs$Treat_num,
        H = Cov,
        pis.hat=NULL,
        mus.reg=NULL,
        depth=2,
        minsplit=20,
        w_vec = cbind(w0,1-w0),
        weight_combine = "mean",
        lambda = 0.05)

treeout
leaf_pred = predict_leaf.DTR(treeout, newdata = Cov)
# table(leaf_pred)
# leaf_n = table(leaf_pred)
tree0 = vis_tree(max_h = 2,treeout,number = table(leaf_pred))
plot(tree0)


map_to_consecutive = function(x) {
  mapped_values = match(x, unique(x))
  return(mapped_values)
}
df_obs$group.MOTree = map_to_consecutive(leaf_pred)
```
### Point Visualization

```{r, warning=FALSE}
class.A = sort(unique(A))
k=K=length(class.A)
# label0 = paste(c("A","B","C","D"),":",class.A,sep="")
label0 = class.A

p_list2 = list()
p_list3 = list()
leaf_vec = sort(unique(leaf_pred))
n_leaf = length(leaf_vec)

for(ii in 1:n_leaf){
  chosen = which(leaf_pred==leaf_vec[ii])
  (p_list2[[ii]] = my_vis_elipse(mu1.hat,
                                 mu2.hat,
                                 chosen,
                                 k=4,ref_k = 1, label=label0,lwd=3,
                                 textsize = 10))
}


# + xlim(-0.3,0.25) + ylim(-0.2,0.3)

plot4 = function(p_list){
  # 2. Save the legend
  legend = get_legend(p_list[[1]])
  
  # 3. Remove the legend from the box plot
  for(ii in 1:n_leaf){
    p_list[[ii]] = p_list[[ii]] + theme(legend.position="none") + 
      ggtitle(paste("Leaf Node",ii,", N=",leaf_n[ii]))
  }
  p1 = p_list[[1]] + theme(legend.position="none") 
  p2 = p_list[[2]] + theme(legend.position="none") 
  p3 = p_list[[3]] + theme(legend.position="none")
  # p4 = p_list[[4]] + theme(legend.position="none")
  
  # 4. Create a blank plot
  blankPlot = ggplot()+geom_blank(aes(1,1)) + 
    cowplot::theme_nothing()

  # p = grid.arrange(p1,p3,legend,p2, legend, ncol=3,
  #              widths=c(5, 5, 2),
  #              top=textGrob("Different Leaf Node's Shape",
  #              gp=gpar(fontsize=15,fontface="bold")))
  p = grid.arrange(p1,p2,p3,legend,
                   ncol=2,
               widths=c(5, 5),
               top=textGrob("Different Leaf Node's Shape",
               gp=gpar(fontsize=15,fontface="bold")))
  
  p
}

# triangle
p = plot4(p_list = p_list2)
#plot_grid(p)
```

# Comparison Matrices

https://nlp.stanford.edu/IR-book/html/htmledition/evaluation-of-clustering-1.html

## YS Examine Performance
Yao's confusion:
which one is makes more sense?

- use all Y and X and A (is that make sense??)
- use Y and X
- use

Simulation code for comparing alternative clustering methods

```{r}
SimuData = df_obs %>% dplyr::select(Y1_obs, Y2_obs, 
                                    # Treat_num, 
                                    starts_with("X"))

```


**K-means clustering**
```{r}
# 3 clusters, use X and Y
kmeans_result3 = kmeans(SimuData, centers = 3)  # Assuming 3 clusters
table(kmeans_result3$cluster)

df_kmeans = data.frame(Y1 = SimuData[,1], Y2 = SimuData[,2], 
                        Cluster = as.factor(kmeans_result3$cluster))
ggplot(df_kmeans, aes(x = Y1, y = Y2, color = Cluster)) +
  geom_point() +
  theme_minimal() +
  labs(title = "K-Means Clustering (k = 3)")



# 4 clusters, use X and Y
kmeans_result4 = kmeans(SimuData, centers = 4)  # Assuming 3 clusters
table(kmeans_result4$cluster)

df_kmeans = data.frame(Y1 = SimuData[,1], Y2 = SimuData[,2], 
                        Cluster = as.factor(kmeans_result4$cluster))
ggplot(df_kmeans, aes(x = Y1, y = Y2, color = Cluster)) +
  geom_point() +
  theme_minimal() +
  labs(title = "K-Means Clustering (k = 4)")

df_obs$group.kmeans3 = kmeans_result3$cluster
df_obs$group.kmeans4 = kmeans_result4$cluster
```


**Hierarchical Clustering**
Two different algorithms are found in the literature for Ward clustering. 

The one used by option "ward.D" (equivalent to the only Ward option "ward" in R versions ≤ 3.0.3) does not implement Ward's (1963) clustering criterion, whereas option "ward.D2" implements that criterion (Murtagh and Legendre 2014). With the latter, the dissimilarities are squared before cluster updating. Note that agnes(*, method="ward") corresponds to hclust(*, "ward.D2").

```{r}
hc_result = hclust(dist(SimuData), method = "ward.D2")
plot(hc_result, labels = FALSE, main = "Dendrogram of Hierarchical Clustering")
# assume 4 clusters
hc_clusters = cutree(hc_result, k = 4)
table(hc_clusters)

df_hc = data.frame(SimuData, Cluster = as.factor(hc_clusters))
ggplot(df_hc, aes(x = Y1_obs, y = Y2_obs, color = Cluster)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Hierarchical Clustering")

df_obs$group.hc = hc_clusters
```



**Gaussian Mixture Model (GMM)**
Model-based clustering based on parameterized finite Gaussian mixture models. Models are estimated by EM algorithm initialized by hierarchical model-based agglomerative clustering. The optimal model is then selected according to BIC.
```{r}
gmm_result = Mclust(SimuData# , 
                     #G = 5
                     )  # Assuming 4 clusters
table(gmm_result$classification)
df_gmm = data.frame(SimuData, Cluster = as.factor(gmm_result$classification))


summary(gmm_result, parameter = T)
# gmm_result$z
ggplot(df_gmm, aes(x = Y1_obs, y = Y2_obs, color = Cluster)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Gaussian Mixture Model (GMM) Clustering")


df_obs$group.gmm = gmm_result$classification 
```


**Spectral Clustering**
A spectral clustering algorithm. Clustering is performed by embedding the data into the subspace of the eigenvectors of an affinity matrix.
```{r}
spectral_result = specc(as.matrix(SimuData), centers = 4)  # Assuming 4 clusters
table(spectral_result)
# spectral_result@.Data
df_spectral = data.frame(SimuData, 
                          Cluster = as.factor(spectral_result@.Data))
ggplot(df_spectral, aes(x = Y1_obs, y = Y2_obs, color = Cluster)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Spectral Clustering")


df_obs$group.spectral = spectral_result@.Data
```


**Self-Organizing Map (SOM)**
```{r}
som_grid = somgrid(xdim = 2, ydim = 2, topo = "rectangular")
som_model = som(as.matrix(SimuData), grid = som_grid, rlen = 100)
som_clusters = cutree(hclust(dist(som_model$codes[[1]])), k = 4)  # Cluster SOM codes

# Assign SOM clusters to data
som_result = som_model$unit.classif
table(som_clusters[som_result])

# Visualize SOM Clustering
df_som = data.frame(SimuData, 
                     Cluster = as.factor(som_clusters[som_result]))
ggplot(df_som, aes(x = Y1_obs, y = Y2_obs, color = Cluster)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Self-Organizing Map (SOM) Clustering")


df_obs$group.som = som_clusters[som_result]
```


######. Examine Performance ######

### Clustering purity measures

**1. Normalized mutual information**
Measures the mutual dependence between the true labels and the predicted clusters, normalized to be between 0 and 1.


**2. Adjusted Rand index (ARI)**

Rand index: Measures the proportion of true positive and true negative decisions in clustering (i.e., correctly grouped or separated pairs).

ARI corrects the Rand Index for chance by adjusting the similarity score based on the expected similarity if clusters were assigned at random.
ARI ranges from -1 to 1, where:

* 1 indicates perfect agreement between the two cluster assignments.
* 0 indicates random labeling.
* Negative values suggest less agreement than expected by chance.

```{r}
true_labels_nmi = as.cl_partition(df_obs$Group)     
true_labels_ari = as.numeric(df_obs$Group)      
clustering_methods = list(
  MOTree = df_obs$group.MOTree,
  KMeans3 = df_obs$group.kmeans3,
  KMeans4 = df_obs$group.kmeans4,
  HC = df_obs$group.hc,
  GMM = df_obs$group.gmm,
  Spectral = df_obs$group.spectral,
  SOM = df_obs$group.som
)
nmi_results = as.list(rep(NA,7))
ari_results = as.list(rep(NA,7))
names(nmi_results) = names(clustering_methods)
names(ari_results) = names(clustering_methods)
dist_matrix = dist(as.matrix(SimuData))# Note: cluster.stats needs a distance matrix - we use Euclidean distance on SimuData

for (method in seq_along(clustering_methods)) {
  method_name = names(clustering_methods)[i]
  pred_labels_nmi = as.cl_partition(clustering_methods[[method_name]])  
  pred_labels_ari = as.numeric(clustering_methods[[method_name]])      
  
  nmi_results[[method]] = as.numeric(cl_agreement(true_labels_nmi, 
                                            pred_labels_nmi, 
                                            method = "NMI"))
  ari_results[[method]] = cluster.stats(dist_matrix, true_labels_ari, 
                                  pred_labels_ari)$corrected.rand
}
nmi_results
ari_results
```


### Counterfactual mean outcome

```{r}
cluster_opt_trt_MOTree = c()
for (cluster in unique(df_obs$group.MOTree)) {
  cluster_ids = which(df_obs$group.MOTree == cluster)
  avg_outcomes = colMeans(Y1[cluster_ids, , drop = FALSE])
  cluster_opt_trt_MOTree[cluster] = which.max(avg_outcomes)
}

df_obs$opt_trt_MOTree = sapply(df_obs$group.MOTree, 
                                function(cluster) cluster_opt_trt_MOTree[cluster])

df_obs$cf_MOTree = sapply(1:nrow(Y1), function(i) Y1[i, df_obs$opt_trt_MOTree[i]])

avg_cf_MOTree = mean(df_obs$cf_MOTree)
avg_cf_MOTree
```

```{r}
# Define the weight sequence
weights <- seq(0, 1, by = 0.1)

# List of clustering methods to evaluate
clustering_methods <- c("group.MOTree", "group.kmeans3", "group.kmeans4", "group.hc", "group.gmm", "group.spectral", "group.som")

# Initialize list to store average counterfactual outcomes for each weight and method
avg_cf_results <- list()

# Loop over each weight combination to create Y_w matrices and calculate results
for (w_idx in seq_along(weights)) {
  # Current weight
  w <- weights[w_idx]
  
  # Step 1: Generate the weighted counterfactual outcome matrix for the current weight
  Y_w <- w * Y1 + (1 - w) * Y2
  
  # Initialize vector to store results for the current weight
  avg_cf_results[[paste0("avg_cf_result", w_idx - 1)]] <- numeric(length(clustering_methods))
  
  # Step 2: Loop over each clustering method
  for (method_idx in seq_along(clustering_methods)) {
    # Get the method name and cluster labels
    method_name <- clustering_methods[method_idx]
    cluster_labels <- df_obs[[method_name]]
    
    # Step 3: Determine the optimal treatment for each cluster in the current method using Y_w
    cluster_opt_trt <- sapply(unique(cluster_labels), function(cluster) {
      cluster_ids <- which(cluster_labels == cluster)
      avg_outcomes <- colMeans(Y_w[cluster_ids, , drop = FALSE])
      which.max(avg_outcomes)  # Optimal treatment with max average outcome
    })
    
    # Step 4: Assign the optimal treatment to each patient based on their cluster
    df_obs[[paste0("opt_trt_", method_name, "_w", w_idx - 1)]] <- sapply(cluster_labels, function(cluster) cluster_opt_trt[as.character(cluster)])
    
    # Step 5: Calculate counterfactual outcome based on the assigned optimal treatment
    df_obs[[paste0("cf_", method_name, "_w", w_idx - 1)]] <- sapply(1:nrow(Y_w), function(i) Y_w[i, df_obs[[paste0("opt_trt_", method_name, "_w", w_idx - 1)]][i]])
    
    # Step 6: Compute and store the average counterfactual mean outcome for the method and weight
    avg_cf_results[[paste0("avg_cf_result", w_idx - 1)]][method_idx] <- mean(df_obs[[paste0("cf_", method_name, "_w", w_idx - 1)]])
  }
}

# Naming each entry in avg_cf_results for clarity
names(avg_cf_results) <- paste0("avg_cf_result", seq_along(weights) - 1)
avg_cf_results
```






###### Archived ####

## YS note: decide not to use this since it is a measure that evaluate the comopatness and separation of the clusteres based on daatr alone, but do not requires the true labels

**Calinski-Harabasz Index (CH)**
Measures the ratio of the sum of between-cluster dispersion to within-cluster dispersion. Higher values indicate better-defined clusters

```{r}
clustering_methods = list(
  MOTree = as.numeric(df_obs$group.MOTree),
  KMeans3 = as.numeric(df_obs$group.kmeans3),
  KMeans4 = as.numeric(df_obs$group.kmeans4),
  HC = as.numeric(df_obs$group.hc),
  GMM = as.numeric(df_obs$group.gmm),
  Spectral = as.numeric(df_obs$group.spectral),
  SOM = as.numeric(df_obs$group.som)
)

# Initialize an empty list to store the CH Index results
ch_index_results = list()

# Loop through each clustering method and calculate the CH Index
for (method_name in names(clustering_methods)) {
  # Extract the predicted labels for the current method
  pred_labels = clustering_methods[[method_name]]
  
  # Calculate the CH Index using cluster.stats
  ch_index = cluster.stats(d = dist_matrix, clustering = pred_labels)$ch
  
  # Store the result in the list
  ch_index_results[[method_name]] = ch_index
}

# Display the Calinski-Harabasz Index results
ch_index_results



```

##### not used 

```{r}
# Prepare a vector to store performance metrics
clustering_methods = c("group.kmeans3", 
                        "group.kmeans4", 
                        "group.hc", 
                        "group.gmm", 
                        "group.spectral", 
                        "group.som")
performance_metrics = data.frame(Method = clustering_methods, 
                                  NMI = NA, 
                                  RI = NA, 
                                  ARI = NA, 
                                  CH_Index = NA)

true_labels = df_obs$Group

for (i in seq_along(clustering_methods)) {
  method = clustering_methods[i]
  pred_labels = df_obs[[method]]  
  
  NMI = clue::NMI(as.numeric(true_labels), as.numeric(pred_labels))$value
  RI = cluster.stats(d = dist(SimuData), as.numeric(true_labels), as.numeric(pred_labels))$corrected.rand
  ARI = cluster.stats(d = dist(SimuData), as.numeric(true_labels), as.numeric(pred_labels))$adj.rand
  
  CHI = calinhara(SimuData, as.numeric(pred_labels), cn = max(pred_labels))
  
  # Store metrics in the data frame
  performance_metrics$NMI[i] = NMI
  performance_metrics$RI[i] = RI
  performance_metrics$ARI[i] = ARI
  performance_metrics$CH_Index[i] = CHI
}

# Display the performance metrics table
performance_metrics
```



# CW original code

Generate Data
```{r}
set.seed(123)
k = 4
n = 100

group = rep(1:4,each = n)
x = rnorm(n*4,0,0.05) + (group-1)/3
x = round(x,3)
plot(density(x,from  =-0.2,to = 1.2))


# group 1: A: (1,0) B: (0,1) C:(-1,0) D:(0,-1)
# group 2: A: (1,0) B: (0,1) C:(0,-1) D:(-1,0)
# group 3: B: (1,0) C: (0,1) D:(-1,0) A:(0,-1)
# group 4: C: (1,0) D: (0,1) A:(-1,0) B:(0,-1)

m1 = c(1,0,0,1,
              -1,0,
              0,-1)

m2 = c(1,0,0,1,
              0,-1,
              -1,0)

m3 = c(0,-1,1,0,0,1,-1,0)

m4 = c(-1,0,0,-1,
              1,0,
              0,1)

list_m = list(m1 = m1,m2 = m2,m3 = m3,m4 = m4)
Y = matrix(0,n*4,2*4)

for(ii in 1:(4*n)){
  ind = group[ii]
  Y[ii,] = list_m[[ind]] + rnorm(8,0,0.2)
}

Y1 = Y[,c(1,3,5,7)]
Y2 = Y[,c(2,4,6,8)]

df_vis = data.frame(y1 = as.vector(Y1),
                    y2 = as.vector(Y2),
                    Treat = rep(c("A","B","C","D"),each = length(Y1)/4),
                    group = rep(group,4))
df_vis$Treat = as.factor(df_vis$Treat)

ggplot(data = df_vis,aes(x = y1,y = y2,col = Treat))+
  geom_point()+
  facet_wrap(~group)+
  ylab("Outcome 2")+
  xlab("Outcome 1")
```

```{r}
w0 = seq(0,1,0.05)
A = sample(c("A","B","C","D"),4*n,replace = TRUE,prob=c(1/4,1/4,1/4,1/4)) 
class.A = sort(unique(A))
H = matrix(x,ncol=1)
n = length(A)


k=K=length(class.A)
m=N=length(A)

label0 = paste(c("A","B","C","D"),":",class.A,sep="")

mu1.hat = Y1
mu2.hat = Y2

treeout = DTRtree(mus.hat = list(Y1,Y2),
        A,H,
        pis.hat=NULL,
        mus.reg=NULL,
        depth=3,
        minsplit=10,w_vec = cbind(w0,1-w0),weight_combine = "mean",lambda = 0.02)

treeout
newdata = H
(leaf_pred = predict_leaf.DTR(treeout, H))
# table(leaf_pred)
leaf_n = table(leaf_pred)

tree0 = vis_tree(max_h = 3,treeout,number = table(leaf_pred))
plot(tree0)
```

Point Visualization
```{R}
p_list2 = list()
p_list3 = list()
leaf_vec = sort(unique(leaf_pred))
n_leaf = length(leaf_vec)



for(ii in 1:n_leaf){
  chosen = which(leaf_pred==leaf_vec[ii])
  (p_list2[[ii]] = my_vis_elipse(mu1.hat,mu2.hat,chosen,
                                 k=4,ref_k = 1, label=label0,lwd=3))
}


# + xlim(-0.3,0.25) + ylim(-0.2,0.3)

plot4 = function(p_list){
  # 2. Save the legend
  legend = get_legend(p_list[[1]])
  
  # 3. Remove the legend from the box plot
  for(ii in 1:n_leaf){
    p_list[[ii]] = p_list[[ii]] + theme(legend.position="none") + 
      ggtitle(paste("Leaf Node",ii,", N=",leaf_n[ii]))
  }
  p1 = p_list[[1]] + theme(legend.position="none") 
  p2 = p_list[[2]] + theme(legend.position="none") 
  p3 = p_list[[3]] + theme(legend.position="none")
  # p4 = p_list[[4]] + theme(legend.position="none")
  
  # 4. Create a blank plot
  blankPlot = ggplot()+geom_blank(aes(1,1)) + 
    cowplot::theme_nothing()
  # pdf(file = "~/Desktop/Multi_Outcome/cluster/LZ_compare/LZ_assumption.pdf",
  #     width = 17.4 / 2.54*1.5, # The width of the plot in inches
  #     height = 17.4 / 2.54 * 0.75) # The height of the plot in inches
  p = grid.arrange(p1,p3,
               legend,p2, legend, ncol=3,
               widths=c(5, 5, 2),
               top=textGrob("Different Leaf Node's Shape",
                            gp=gpar(fontsize=18,fontface="bold")))
  p
}

# triangle
p = plot4(p_list = p_list2)
#plot_grid(p)
```


