---
title: "multiple tree clustering toy example"
output: html_document
date: '2024-04-04'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggpubr)
library(ggplot2)
library(gridExtra)
library(cowplot)
library(grid)
library(DiagrammeR)
library(nnet)
# for performance comparison
library(mclust)
library(kernlab)
library(kohonen)
library(class)
library(mclust)
library(clue) # NMI
library(cluster)
library(fpc) # RI
library(tibble)
library(dplyr)
library(tidyr)
library(MOTRL)

setwd("R")
source("Benefit_gain.R")
source("best.H.R")
source("MO_Tree_Chang.R")
source("predict_leaf.R")
source("Reg.mu.R")
source("Split.X.R")
source("visualization.R")
source("vis_tree.R")

source("mus.AIPW.R")
source("M.propen.R")
Custom.color = c("#CD2626","#79aec1","#2E8B57","#d6b55a")

map_to_consecutive = function(x) {
  mapped_values = match(x, unique(x))
  return(mapped_values)
}
```


## YS update simulation function with iterations 11/3/2024

4 Treatment case
```{r}
Simulation_MOTree = function(iter = 100, n.cov = 5, n.per.group = 100) {
  nmi_results = rep(list(rep(NA, iter)),7) 
  ari_results = rep(list(rep(NA, iter)),7) 
  # non_dominant_results <- rep(list(rep(NA, iter)), 7)  # New performance metric

  weights = seq(0, 1, by = 0.1)
  for (w_idx in seq_along(weights)) {
    assign(paste0("avg_cf_results", w_idx - 1), rep(list(rep(NA, iter)),7) )
    # assign(paste0("obs_weighted_mean", w_idx - 1), numeric(iter))
    assign(paste0("true_optimal_weighted_mean", w_idx - 1), numeric(iter))  
    
    # new
    assign(paste0("non_dominant_results", w_idx - 1), rep(list(rep(NA, iter)), 7))  # New for non-dominance
    
  }
  
  for (i in c(1:iter)) {
    
    ###########################################
    ############ Data generation ##############
    ###########################################
    set.seed(412 + i)
    k = 4
    group = rep(1:4, each = n.per.group)
    X = matrix(NA, nrow = n.per.group * 4, ncol = n.cov)
    X[, 1] = rnorm(n.per.group*4,0,0.05) + (group-1)/3
    X[, 2] = rnorm(n.per.group * 4, mean = 0, sd = 0.05) - 0.5 * (group - 2) 
    for (k in 3:n.cov) {
      X[, k] = rnorm(n.per.group * 4, mean = 0, sd = 0.05)
    }
    m1 = c(1, 0, 0, 1, -1, 0, 0, -1)
    m2 = c(1, 0, 0, 1, 0, -1, -1, 0)
    m3 = c(0, -1, 1, 0, 0, 1, -1, 0)
    m4 = c(-1, 0, 0, -1, 1, 0, 0, 1)
    list_m = list(m1 = m1, m2 = m2, m3 = m3, m4 = m4)
    Y = matrix(0, n.per.group * 4, 2 * 4)
    for (ii in 1:(4 * n.per.group)) {
      ind = group[ii]
      Y[ii, ] = list_m[[ind]] + 
                X[ii, 1] * 0.1 +  
                X[ii, 2] * 0.05 +  
                X[ii, 3] * -0.0005 + 
                X[ii, 4] * 0.0001 +  
                X[ii, 5] * -0.0001 + 
                rnorm(8, 0, 0.3)  
    }
    Y1 = Y[, c(1, 3, 5, 7)]
    Y2 = Y[, c(2, 4, 6, 8)]
    
    true_treatment = sample(1:4, n.per.group * 4, replace = TRUE)
    Y1.obs = sapply(1:(n.per.group * 4), function(i) Y1[i, true_treatment[i]])
    Y2.obs = sapply(1:(n.per.group * 4), function(i) Y2[i, true_treatment[i]])
    
    df_obs = data.frame(
      Y1_obs = Y1.obs,
      Y2_obs = Y2.obs,
      Treat_num = true_treatment,
      Group = factor(group)
    )
    df_obs$true_Group = case_when(df_obs$Group == 1 | df_obs$Group == 2 ~ 1,
                                  df_obs$Group == 3 ~ 2,
                                  df_obs$Group == 4 ~ 3)
    
    df_obs$Treatment = as.factor(case_when(df_obs$Treat_num == 1 ~ "A",
                                           df_obs$Treat_num == 2 ~ "B",
                                           df_obs$Treat_num == 3 ~ "C",
                                           df_obs$Treat_num == 4 ~ "D"))
    for (cov in 1:n.cov) {
      df_obs[[paste0("X", cov)]] = X[, cov]
    }
    
    # 11/11/2024
    # YS add this for new metric on dominance
    non_dominant_treatments <- lapply(seq_len(n.per.group * 4), function(patient) {
      outcomes <- cbind(Y1[patient, ], Y2[patient, ])
      is_non_dominated <- function(outcomes) {
        apply(outcomes, 1, function(x) {
          !any(apply(outcomes, 1, function(y) all(y >= x) & any(y > x)))
        })
      }
      
      pareto_front <- which(is_non_dominated(outcomes))
      return(pareto_front)  
    })
    
    ## YS add true optimal weighted conterfactual mean
    for (w_idx in seq_along(weights)) {
      w <- weights[w_idx]
      
      # Weighted counterfactual outcomes for all treatments
      Y_w <- w * Y1 + (1 - w) * Y2
      
      # Maximum weighted counterfactual outcome for each individual
      max_weighted_outcomes <- apply(Y_w, 1, max)
      assign(paste0("true_optimal_weighted_mean", w_idx - 1),
             replace(get(paste0("true_optimal_weighted_mean", w_idx - 1)), i, mean(max_weighted_outcomes)))
      
      # Observed mean weighted outcome
      # weighted_obs <- w * Y1.obs + (1 - w) * Y2.obs
      # assign(paste0("obs_weighted_mean", w_idx - 1), 
      #        replace(get(paste0("obs_weighted_mean", w_idx - 1)), i, mean(weighted_obs)))
    }
    
    
    
    ###########################################
    ########## Clustering methods #############
    ###########################################
    
    ## MOTree
    w0 = seq(0,1,0.02) 
    Cov = df_obs %>% dplyr::select(starts_with("X"))
    treeout = DTRtree(Ys = cbind(df_obs$Y1_obs, df_obs$Y2_obs), 
            A = df_obs$Treat_num,
            H = Cov,
            pis.hat=NULL,
            mus.reg=NULL,
            depth=2,
            minsplit=20,
            w_vec = cbind(w0,1-w0),
            weight_combine = "mean",
            lambda = 0.05)
    leaf_pred = predict_leaf.DTR(treeout, newdata = Cov)
    df_obs$group.MOTree = map_to_consecutive(leaf_pred)
    
    SimuData = df_obs %>% dplyr::select(# Y1_obs, Y2_obs, 
                                        # Treat_num, 
                                        starts_with("X"))
    
    ## K-means 
    kmeans_result3 = kmeans(SimuData, centers = 3)  # Assuming 3 clusters
    kmeans_result4 = kmeans(SimuData, centers = 4)  # Assuming 3 clusters
    df_obs$group.kmeans3 = kmeans_result3$cluster
    df_obs$group.kmeans4 = kmeans_result4$cluster
    
    ## Hierarchical
    hc_result = hclust(dist(SimuData), method = "ward.D") # "ward.D2")
    hc_clusters = cutree(hc_result, k = 3) # k = 4)
    df_obs$group.hc = hc_clusters
    
    ## GMM
    gmm_result = Mclust(SimuData) 
    df_obs$group.gmm = gmm_result$classification 
    
    ## Spectral Clustering
    spectral_result = specc(as.matrix(SimuData), centers = 4)  # Assuming 4 clusters
    df_obs$group.spectral = spectral_result@.Data
    
    ## Self-Organizing Map (SOM)
    som_grid = kohonen::somgrid(xdim = 2, ydim = 2, topo = "rectangular")
    som_model = kohonen::som(as.matrix(SimuData), grid = som_grid, rlen = 100)
    som_clusters = cutree(hclust(dist(som_model$codes[[1]])), k = 4)  
    som_result = som_model$unit.classif
    df_obs$group.som = som_clusters[som_result]
    
    ###########################################
    ############ Begin comparison #############
    ###########################################
    true_labels_nmi = as.cl_partition(df_obs$true_Group)     
    true_labels_ari = as.numeric(df_obs$true_Group)      
    clustering_methods = list(
      MOTree = df_obs$group.MOTree,
      MOTRL = NA,
      HC = df_obs$group.hc,
      GMM = df_obs$group.gmm,
      KMeans3 = df_obs$group.kmeans3,
      KMeans4 = df_obs$group.kmeans4,
      Spectral = df_obs$group.spectral,
      SOM = df_obs$group.som
      
    )

    dist_matrix = dist(as.matrix(SimuData))
    
    for (method in seq_along(clustering_methods)) {
      method_name = names(clustering_methods)[method]
      pred_labels_nmi = as.cl_partition(clustering_methods[[method_name]])  
      pred_labels_ari = as.numeric(clustering_methods[[method_name]])    
      cluster_labels = as.numeric(clustering_methods[[method_name]])      
      nmi_results[[method]][i] = as.numeric(cl_agreement(true_labels_nmi, 
                                                pred_labels_nmi, 
                                                method = "NMI"))
      ari_results[[method]][i] = cluster.stats(dist_matrix, true_labels_ari, 
                                      pred_labels_ari)$corrected.rand
    
      cluster_opt_trt = list()
      for (w_idx in seq_along(weights)) {
          w = weights[w_idx]
          Y_w = w * Y1 + (1 - w) * Y2
          
          # new: output observed mean outcome
          # weighted_obs = w * Y1.obs + (1 - w) * Y2.obs
          # assign(paste0("obs_weighted_mean", w_idx - 1), 
          #    replace(get(paste0("obs_weighted_mean", w_idx - 1)), i, mean(weighted_obs)))
          # 
          # 
          # find cluster-based optimal treatment for each individual (by each of the methods)
          cluster_opt_trt[[method]] = sapply(unique(cluster_labels), 
             function(cluster) {
                cluster_ids = which(cluster_labels == cluster)
                avg_outcomes = colMeans(Y_w[cluster_ids, , drop = FALSE])
                which.max(avg_outcomes)  
              })

          df_obs[[paste0("opt_trt_", method_name, "_w", w_idx - 1)]] = sapply(cluster_labels,
                function(cluster) cluster_opt_trt[[method]][cluster]) 
          df_obs[[paste0("cf_", method_name, "_w", w_idx - 1)]] = sapply(1:nrow(Y_w), 
                function(x) Y_w[x, df_obs[[paste0("opt_trt_", method_name, "_w", w_idx - 1)]][x]])
          
          avg_cf_results <- get(paste0("avg_cf_results", w_idx - 1))
          avg_cf_results[[method]][i] <- mean(df_obs[[paste0("cf_", method_name, "_w", w_idx - 1)]])
          assign(paste0("avg_cf_results", w_idx - 1), avg_cf_results)

  
          
          ## YS ADD THIS NEW FOR NEW MATRIC 11/25/2024
          ## Predicted optimal treatment for current weight
          pred_opt_trt <- df_obs[[paste0("opt_trt_", method_name, "_w", w_idx - 1)]]
          is_non_dominant <- sapply(seq_len(n.per.group * 4), function(patient) {
            pred_opt_trt[patient] %in% non_dominant_treatments[[patient]]
          })
          non_dominant_results <- get(paste0("non_dominant_results", w_idx - 1))
          non_dominant_results[[method]][i] <- mean(is_non_dominant)
          assign(paste0("non_dominant_results", w_idx - 1), non_dominant_results)
          
          cluster_opt_trt = list() 
          
      }
    
    }
    
    
    
  }
  
  # evaluation
  nmi_mean = round(as.numeric(lapply(nmi_results, mean)),3)
  nmi_sd = round(as.numeric(lapply(nmi_results, sd)),3)
  ari_mean = round(as.numeric(lapply(ari_results, mean)),3)
  ari_sd = round(as.numeric(lapply(ari_results, sd)),3)
  
  nmi_out = paste0(nmi_mean, "(", nmi_sd, ")")
  ari_out = paste0(ari_mean, "(", ari_sd, ")")
  
  # YS add this new 
  non_dominant_summary <- matrix(NA, nrow = 7, ncol = length(weights))
  rownames(non_dominant_summary) <- paste0("Method_", 1:7)  # Adjust according to actual method names
  colnames(non_dominant_summary) <- paste0("Weight_", weights)

  for (w_idx in seq_along(weights)) {
     avg_cf_results <- get(paste0("avg_cf_results", w_idx - 1))
     assign(paste0("avg_cf_mean", w_idx - 1), round(as.numeric(lapply(avg_cf_results, mean)), 3))
     assign(paste0("avg_cf_sd", w_idx - 1), round(as.numeric(lapply(avg_cf_results, sd)), 3))
     assign(paste0("avg_cf_out", w_idx - 1), paste0(get(paste0("avg_cf_mean", w_idx - 1)), 
                                                      "(", get(paste0("avg_cf_sd", w_idx - 1)), ")"))
  
     # for new metric 11/25/2024
     non_dominant_means <- get(paste0("non_dominant_results", w_idx - 1)) # [[method]]
     # non_dominant_summary[method, w_idx] <- mean(non_dominant_means)
     assign(paste0("non_dominant_mean", w_idx - 1), round(as.numeric(lapply(non_dominant_means, mean)), 3))
     assign(paste0("non_dominant_sd", w_idx - 1), round(as.numeric(lapply(non_dominant_means, sd)), 3))
     assign(paste0("non_dominant_out", w_idx - 1), paste0(get(paste0("non_dominant_mean", w_idx - 1)), 
                                                      "(", get(paste0("non_dominant_sd", w_idx - 1)), ")"))
     }
  
  # new
  # obs_weighted_means <- sapply(0:10, function(w_idx) {
  # mean(get(paste0("obs_weighted_mean", w_idx)))
  # })
  # obs_weighted_means <- t(data.frame(obs_weighted_means))
  # rownames(obs_weighted_means) <- "Observed_Mean"
  # colnames(obs_weighted_means) <- paste0("Weight_", seq(0, 1, by = 0.1))
  
  
  true_optimal_weighted_means <- sapply(0:10, function(w_idx) {
    mean(get(paste0("true_optimal_weighted_mean", w_idx)))
  })
  true_optimal_weighted_means <- t(data.frame(true_optimal_weighted_means))
  rownames(true_optimal_weighted_means) <- "True_Optimal_Mean"
  colnames(true_optimal_weighted_means) <- paste0("Weight_", seq(0, 1, by = 0.1))
  
  
  
  clust_perform = data.frame(NMI = nmi_out,
                      ARI = ari_out)
  row.names(clust_perform) = names(clustering_methods)
  
  cf_Y_perform = data.frame(
                      avg_cf_w0 = avg_cf_out0,
                      avg_cf_w1 = avg_cf_out1,
                      avg_cf_w2 = avg_cf_out2,
                      avg_cf_w3 = avg_cf_out3,
                      avg_cf_w4 = avg_cf_out4,
                      avg_cf_w5 = avg_cf_out5,
                      avg_cf_w6 = avg_cf_out6,
                      avg_cf_w7 = avg_cf_out7,
                      avg_cf_w8 = avg_cf_out8,
                      avg_cf_w9 = avg_cf_out9,
                      avg_cf_w10 = avg_cf_out10)
  row.names(cf_Y_perform) = names(clustering_methods)

  
  
  non_dominant_perform = data.frame(
                      non_dominant_w0 = non_dominant_out0,
                      non_dominant_w1 = non_dominant_out1,
                      non_dominant_w2 = non_dominant_out2,
                      non_dominant_w3 = non_dominant_out3,
                      non_dominant_w4 = non_dominant_out4,
                      non_dominant_w5 = non_dominant_out5,
                      non_dominant_w6 = non_dominant_out6,
                      non_dominant_w7 = non_dominant_out7,
                      non_dominant_w8 = non_dominant_out8,
                      non_dominant_w9 = non_dominant_out9,
                      non_dominant_w10 = non_dominant_out10)
  row.names(non_dominant_perform) = names(clustering_methods)
  
  cf_Y_names = c(paste0("avg_cf_mean", 0:10), paste0("avg_cf_sd", 0:10))
  cf_Y = as.data.frame(mget(cf_Y_names))
  row.names(cf_Y) = names(clustering_methods)
  
  # new: Yopt - Yhat
  # Diff_Yopt_Yhat = apply(cf_Y, 1, function(x) {x - true_optimal_weighted_means})
  
  # new
  non_dominant_names = c(paste0("non_dominant_mean", 0:10), paste0("non_dominant_sd", 0:10))
  non_dominant = as.data.frame(mget(non_dominant_names))
  row.names(non_dominant) = names(clustering_methods)
  
  
  return(list(clust_perform = clust_perform,
              cf_Y_perform = cf_Y_perform,
              non_dominant_perform = non_dominant_perform,
              
              cf_Y = cf_Y,
              # obs_weighted_means = obs_weighted_means,
              true_optimal_weighted_means = true_optimal_weighted_means,
              non_dominant = non_dominant
))
}
  

# smaller sample size
result50 = Simulation_MOTree(iter = 100, n.cov = 5, n.per.group = 50)

# larger sample size
result100 = Simulation_MOTree(iter = 100, n.cov = 5, n.per.group = 100)

# larger sample size
result200 = Simulation_MOTree(iter = 100, n.cov = 5, n.per.group = 200)
```

## performance Evaluation

### Clustering Performance

```{r}
result50$clust_perform
result50$cf_Y_perform
result50$non_dominant_perform
```

```{r}
result100$clust_perform
result100$cf_Y_perform
result100$non_dominant_perform
```

```{r}
result500$clust_perform
result500$cf_Y_perform
result500$non_dominant_perform
```

### Visualization

Sample size = 4 * 50

$$Y_w^{*opt} - \hat Y_w^*$$
```{r}
# Extract outcomes from the simulation results
outcomes <- result50$cf_Y  # Counterfactual outcomes
true_opt_means <- result50$true_optimal_weighted_means  # 1x11 matrix of observed weighted outcomes

# Prepare the observed means for merging
true_opt_long <- as.data.frame(t(true_opt_means)) %>%
  rownames_to_column(var = "Weight") %>%
  rename(TrueOpt = True_Optimal_Mean) %>%
  mutate(Weight = as.numeric(gsub("Weight_", "", Weight)))

# Prepare the counterfactual mean outcomes and merge with observed means
outcomes_long <- outcomes %>%
  rownames_to_column(var = "Method") %>%
  pivot_longer(cols = starts_with("avg_cf_mean"), 
               names_to = "Weight", 
               values_to = "Mean") %>%
  mutate(Weight = as.numeric(gsub("avg_cf_mean", "", Weight)) * 0.1) %>%
  left_join(true_opt_long, by = "Weight") %>%
  mutate(Difference = Mean - TrueOpt)  # Calculate the difference between counterfactual and observed means

# Plot the differences
ggplot(outcomes_long, aes(x = Weight, y = Difference, color = Method, fill = Method)) +
  geom_smooth(method = "loess", se = TRUE, size = 1.2) +  # Smoothed line with CI for difference
  labs(title = "Difference between Estimated and True Optimal Conterfactual Outcome",
       x = "Weight on Y1",
       y = "Difference (Y_opt - Y_hat)") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )


```



```{r}
# Extract the non-dominant data from the simulation results
non_dominant <- result50$non_dominant

# Prepare the non-dominant data for plotting
non_dominant_long <- non_dominant %>%
  rownames_to_column(var = "Method") %>%
  pivot_longer(cols = starts_with("non_dominant_mean"), 
               names_to = "Weight", 
               values_to = "Mean") %>%
  mutate(Weight = as.numeric(gsub("non_dominant_mean", "", Weight)) * 0.1) %>%
  left_join(
    non_dominant %>%
      rownames_to_column(var = "Method") %>%
      pivot_longer(cols = starts_with("non_dominant_sd"), 
                   names_to = "Weight", 
                   values_to = "SD") %>%
      mutate(Weight = as.numeric(gsub("non_dominant_sd", "", Weight)) * 0.1),
    by = c("Method", "Weight")
  )

# Plot the percentage of non-dominance
ggplot(non_dominant_long, aes(x = Weight, y = Mean, color = Method, fill = Method)) +
  geom_line(size = 1.2) +  # Line for the mean percentage of non-dominance
  geom_ribbon(aes(ymin = Mean - 1.96*SD/sqrt(200), ymax = Mean + 1.96*SD/sqrt(200)), alpha = 0.2, linetype = 0) +  # Add shadow for SD
  labs(title = "Percentage of Non-Dominance of the Estimated Optimal Treatment",
       x = "Weight on Y1",
       y = "Percentage of Non-Dominance") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )

```




Sample size = 4 * 500

$$Y_w^{*opt} - \hat Y_w^*$$
```{r}
# Extract outcomes from the simulation results
outcomes <- result500$cf_Y  # Counterfactual outcomes
true_opt_means <- result500$true_optimal_weighted_means  # 1x11 matrix of observed weighted outcomes

# Prepare the observed means for merging
true_opt_long <- as.data.frame(t(true_opt_means)) %>%
  rownames_to_column(var = "Weight") %>%
  rename(TrueOpt = True_Optimal_Mean) %>%
  mutate(Weight = as.numeric(gsub("Weight_", "", Weight)))

# Prepare the counterfactual mean outcomes and merge with observed means
outcomes_long <- outcomes %>%
  rownames_to_column(var = "Method") %>%
  pivot_longer(cols = starts_with("avg_cf_mean"), 
               names_to = "Weight", 
               values_to = "Mean") %>%
  mutate(Weight = as.numeric(gsub("avg_cf_mean", "", Weight)) * 0.1) %>%
  left_join(true_opt_long, by = "Weight") %>%
  mutate(Difference = Mean - TrueOpt)  # Calculate the difference between counterfactual and observed means

# Plot the differences
ggplot(outcomes_long, aes(x = Weight, y = Difference, color = Method, fill = Method)) +
  geom_smooth(method = "loess", se = TRUE, size = 1.2) +  # Smoothed line with CI for difference
  labs(title = "Difference between Estimated and True Optimal Conterfactual Outcome",
       x = "Weight on Y1",
       y = "Difference (Y_opt - Y_hat)") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )


```



```{r}
# Extract the non-dominant data from the simulation results
non_dominant <- result500$non_dominant

# Prepare the non-dominant data for plotting
non_dominant_long <- non_dominant %>%
  rownames_to_column(var = "Method") %>%
  pivot_longer(cols = starts_with("non_dominant_mean"), 
               names_to = "Weight", 
               values_to = "Mean") %>%
  mutate(Weight = as.numeric(gsub("non_dominant_mean", "", Weight)) * 0.1) %>%
  left_join(
    non_dominant %>%
      rownames_to_column(var = "Method") %>%
      pivot_longer(cols = starts_with("non_dominant_sd"), 
                   names_to = "Weight", 
                   values_to = "SD") %>%
      mutate(Weight = as.numeric(gsub("non_dominant_sd", "", Weight)) * 0.1),
    by = c("Method", "Weight")
  )

# Plot the percentage of non-dominance
ggplot(non_dominant_long, aes(x = Weight, y = Mean, color = Method, fill = Method)) +
  geom_line(size = 1.2) +  # Line for the mean percentage of non-dominance
  geom_ribbon(aes(ymin = Mean - 1.96*SD/sqrt(200), ymax = Mean + 1.96*SD/sqrt(200)), alpha = 0.2, linetype = 0) +  # Add shadow for SD
  labs(title = "Percentage of Non-Dominance of the Estimated Optimal Treatment",
       x = "Weight on Y1",
       y = "Percentage of Non-Dominance") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )

```










# 11/05/2024 YS to do:

Change the outcome presentation

X - [Figure 1] Change figure to Y_opt - Y_hat 

X - [Figure 2] Percentage of non-dominance


- [add a row in Table 1 for MOTRL?] compare with MOTRL across different weights



Add more scenarios

- [add to Table 1 as new chunks] design other scenarios with different sample size? noise? covaraite structure

  Sample sizes: 50, 500, 1000
  Current noise: Normal(0, 0.3)
  Current covaraites: 5
  
- [add a new distribution of true conterfactual] e.g. add a setup with 8 treatments


- ? [Table 2 / Figure 2] simple example for the 3 outcome case


# Archived code

Visualize weighted counterfactual mean
```{r}
outcomes = result$cf_Y

outcomes_long <- outcomes %>%
  rownames_to_column(var = "Method") %>%
  pivot_longer(cols = starts_with("avg_cf_mean"), 
               names_to = "Weight", 
               values_to = "Mean") %>%
  mutate(Weight = as.numeric(gsub("avg_cf_mean", "", Weight)) * 0.1) %>%
  left_join(outcomes %>%
              rownames_to_column(var = "Method") %>%
              pivot_longer(cols = starts_with("avg_cf_sd"), 
                           names_to = "Weight", 
                           values_to = "SD") %>%
              mutate(Weight = as.numeric(gsub("avg_cf_sd", "", Weight)) * 0.1),
            by = c("Method", "Weight"))

ggplot(outcomes_long, aes(x = Weight, y = Mean, color = Method, fill = Method)) +
  geom_smooth(method = "loess", se = TRUE, size = 1.2) +  # Only smoothed line with CI
  # scale_x_continuous(breaks = weights, labels = scales::percent(weights)) +
  labs(title = "Counterfactual mean outcome under different weights",
       x = "Weight on Y1",
       y = "Counterfactual mean outcome") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )

```



simulation function

```{r}
weights <- seq(0, 1, by = 0.1)
outcomes_long <- outcomes %>%
  rownames_to_column(var = "Method") %>%
  pivot_longer(cols = starts_with("avg_cf_mean"), 
               names_to = "Weight", 
               values_to = "Mean") %>%
  mutate(Weight = as.numeric(gsub("avg_cf_mean", "", Weight)) * 0.1) %>%
  left_join(outcomes %>%
              rownames_to_column(var = "Method") %>%
              pivot_longer(cols = starts_with("avg_cf_sd"), 
                           names_to = "Weight", 
                           values_to = "SD") %>%
              mutate(Weight = as.numeric(gsub("avg_cf_sd", "", Weight)) * 0.1),
            by = c("Method", "Weight"))
ggplot(outcomes_long, aes(x = Weight, y = Mean, color = Method, fill = Method)) +
  geom_line(size = 1.1) +
  geom_ribbon(aes(ymin = Mean - SD, ymax = Mean + SD), alpha = 0.2) +
  scale_x_continuous(breaks = weights, labels = scales::percent(weights)) +
  labs(title = "Counterfactual Mean Outcome Under Different Weights",
       x = "Weight",
       y = "Counterfactual mean outcome") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  ) +
  geom_smooth(aes(y = Mean), method = "loess", se = FALSE, size = 1, linetype = "dashed")

```

```{r}
sample_size = 400
outcomes_long <- outcomes %>%
  rownames_to_column(var = "Method") %>%
  pivot_longer(cols = starts_with("avg_cf_mean"), 
               names_to = "Weight", 
               values_to = "Mean") %>%
  mutate(Weight = as.numeric(gsub("avg_cf_mean", "", Weight)) * 0.1) %>%
  left_join(outcomes %>%
              rownames_to_column(var = "Method") %>%
              pivot_longer(cols = starts_with("avg_cf_sd"), 
                           names_to = "Weight", 
                           values_to = "SD") %>%
              mutate(Weight = as.numeric(gsub("avg_cf_sd", "", Weight)) * 0.1),
            by = c("Method", "Weight")) %>%
  mutate(CI = 1.96 * SD / sqrt(sample_size))  # Calculate 95% CI

ggplot(outcomes_long, aes(x = Weight, y = Mean, color = Method, fill = Method)) +
  # geom_line(size = 1.1) +
  geom_ribbon(aes(ymin = Mean - CI, ymax = Mean + CI), alpha = 0.2) +
  scale_x_continuous(breaks = weights, labels = scales::percent(weights)) +
  labs(title = "Counterfactual mean outcome under different weights",
       x = "Weight",
       y = "Counterfactual mean outcome") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  ) +
  geom_smooth(aes(y = Mean), method = "loess", se = FALSE, size = 1, linetype = "dashed")
```

